\textbf{NBA Party}

### 2017-07-08 cardinal_analytx_presentation/nightlife_and_sports.tex
Regained significance; added a seasonal trend.

\begin{frame}   \frametitle{Results: NBA}
  \vspace{-2pt}
  \centering
  \tiny{ % m0, m1
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Meet the Spread} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Party discrete & $-$0.555$^{***}$ &  \\    & p = 0.0002 &  \\    & & \\   Party continuous &  & $-$0.153 \\    &  & p = 0.107 \\    & & \\   Lag changes in posession & 0.001 & 0.001 \\    & p = 0.346 & p = 0.373 \\    & & \\   Logged travel distance & $-$0.014 & $-$0.009 \\    & p = 0.577 & p = 0.733 \\    & & \\   East-west travel direction & $-$0.074 & $-$0.039 \\    & p = 0.754 & p = 0.867 \\    & & \\   Number hours rest time & 0.001 & 0.001 \\    & p = 0.218 & p = 0.295 \\    & & \\   Time of game during day & 0.007 & 0.005 \\    & p = 0.603 & p = 0.715 \\    & & \\   Home team effect & 0.002 & 0.004 \\    & p = 0.960 & p = 0.936 \\    & & \\   Logged travel distance * east-west & 0.012 & 0.007 \\    & p = 0.749 & p = 0.846 \\    & & \\   Constant & $-$0.247 & $-$0.229 \\    & p = 0.443 & p = 0.477 \\    & & \\  \hline \\[-1.8ex]  Observations & 9,517 & 9,517 \\  Log Likelihood & $-$6,587.456 & $-$6,593.324 \\  Akaike Inf. Crit. & 13,192.910 & 13,204.650 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}    }   
\end{frame}

\begin{frame}   \frametitle{Placebo test (discrete indicator): what if players rest?}
  \centering
  \tiny{ % mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   Party placebo & 0.056 \\    & p = 0.504 \\    & \\   Lag changes in posession & 0.001 \\    & p = 0.408 \\    & \\   Logged travel distance & $-$0.003 \\    & p = 0.920 \\    & \\   East-west travel direction & $-$0.036 \\    & p = 0.880 \\    & \\   Number hours rest time & 0.001$^{*}$ \\    & p = 0.098 \\    & \\   Time of game during day & 0.003 \\    & p = 0.827 \\    & \\   Home team effect & $-$0.006 \\    & p = 0.896 \\    & \\   Logged travel distance * east-west & 0.006 \\    & p = 0.866 \\    & \\   Constant & $-$0.257 \\    & p = 0.425 \\    & \\  \hline \\[-1.8ex]  Observations & 9,517 \\  Log Likelihood & $-$6,594.404 \\  Akaike Inf. Crit. & 13,206.810 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}      }
\end{frame}

@@

\begin{frame}   \frametitle{Results: MLB}
  \centering
  \tiny{ % m3, m4
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Probability of Winning} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Continuous measure of nightlife & $-$0.120$^{*}$ &  \\    & p = 0.091 &  \\    & & \\   Nightlife (no weekend interaction) &  & 0.137 \\    &  & p = 0.307 \\    & & \\   Bookmaker's odds & 2.682$^{***}$ & 2.669$^{***}$ \\    & p = 0.000 & p = 0.000 \\    & & \\   Home-team effect & 0.014 & 0.144 \\    & p = 0.674 & p = 0.159 \\    & & \\   Number of rest days & 0.018 & 0.016 \\    & p = 0.399 & p = 0.456 \\    & & \\   Logged travel distance & $-$0.005 & $-$0.003 \\    & p = 0.377 & p = 0.519 \\    & & \\   Weekend & 0.044 & 0.002 \\    & p = 0.246 & p = 0.935 \\    & & \\   Constant & $-$1.360$^{***}$ & $-$1.468$^{***}$ \\    & p = 0.000 & p = 0.000 \\    & & \\  \hline \\[-1.8ex]  Observations & 26,473 & 26,473 \\  Log Likelihood & $-$18,124.390 & $-$18,125.300 \\  Akaike Inf. Crit. & 36,262.780 & 36,264.600 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}    } 
\end{frame}

@@

\begin{frame}   \frametitle{Defense in the NBA}
  \begin{adjustwidth}{-.75cm}{}
  \tiny{  % mpa
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & Points Admitted by Team & Team Points Admitted & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.817$^{***}$ &  &  \\    & p = 0.0001 &  &  \\    & & & \\   Continuous party measure &  & 1.803$^{***}$ & $-$0.160 \\    &  & p = 0.007 & p = 0.806 \\    & & & \\   Lag change in possessions &  & 0.118$^{***}$ & 0.115$^{***}$ \\    &  & p = 0.000 & p = 0.000 \\    & & & \\   Logged travel distance &  & $-$0.568$^{***}$ & 0.037 \\    &  & p = 0.005 & p = 0.852 \\    & & & \\   Number hours since last game &  & 0.011 & 0.018$^{**}$ \\    &  & p = 0.115 & p = 0.013 \\    & & & \\   Constant & $-$0.046 & 89.567$^{***}$ & 86.136$^{***}$ \\    & p = 0.612 & p = 0.000 & p = 0.000 \\    & & & \\  \hline \\[-1.8ex]  Observations & 15,139 & 6,234 & 6,234 \\  R$^{2}$ & 0.001 & 0.023 & 0.021 \\  Adjusted R$^{2}$ & 0.001 & 0.023 & 0.021 \\  Residual Std. Error & 11.137 (df = 15137) & 12.071 (df = 6229) & 11.910 (df = 6229) \\  F Statistic & 15.670$^{***}$ (df = 1; 15137) & 37.032$^{***}$ (df = 4; 6229) & 33.756$^{***}$ (df = 4; 6229) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}    }
\end{adjustwidth} 
\end{frame}

>>>>

\begin{frame}   \frametitle{Results: NBA}
  \vspace{-2pt}
  \centering
  \tiny{ % m0, m1
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Meet the Spread} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Party discrete & $-$0.557$^{***}$ &  \\    & (0.149) &  \\    & & \\   Party continuous &  & $-$0.158$^{*}$ \\    &  & (0.095) \\    & & \\   Lag changes in posession & 0.189 & 0.181 \\    & (0.140) & (0.140) \\    & & \\   Logged travel distance & $-$0.015 & $-$0.010 \\    & (0.026) & (0.026) \\    & & \\   East-west travel direction & $-$0.072 & $-$0.037 \\    & (0.234) & (0.234) \\    & & \\   Number hours rest time & 0.001 & 0.001 \\    & (0.001) & (0.001) \\    & & \\   Time of game during day & 0.006 & 0.004 \\    & (0.013) & (0.013) \\    & & \\   Home team effect & 0.002 & 0.004 \\    & (0.044) & (0.044) \\    & & \\   Logged travel distance * east-west & 0.011 & 0.007 \\    & (0.036) & (0.036) \\    & & \\   Constant & $-$0.923 & $-$0.875 \\    & (0.695) & (0.695) \\    & & \\  \hline \\[-1.8ex]  Observations & 9,517 & 9,517 \\  Log Likelihood & $-$6,586.320 & $-$6,592.159 \\  Akaike Inf. Crit. & 13,200.640 & 13,212.320 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular} 
}   
\end{frame}

\begin{frame}   \frametitle{Placebo test (discrete indicator): what if players rest?}
  \centering
  \tiny{ % mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   Party placebo & 0.053 \\    & (0.084) \\    & \\   Lag changes in posession & 0.170 \\    & (0.140) \\    & \\   Logged travel distance & $-$0.004 \\    & (0.026) \\    & \\   East-west travel direction & $-$0.034 \\    & (0.235) \\    & \\   Number hours rest time & 0.001$^{*}$ \\    & (0.001) \\    & \\   Time of game during day & 0.002 \\    & (0.013) \\    & \\   Home team effect & $-$0.006 \\    & (0.044) \\    & \\   Logged travel distance * east-west & 0.006 \\    & (0.036) \\    & \\   Constant & $-$0.865 \\    & (0.695) \\    & \\  \hline \\[-1.8ex]  Observations & 9,517 \\  Log Likelihood & $-$6,593.344 \\  Akaike Inf. Crit. & 13,214.690 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular} 
      }
\end{frame}

@@

\begin{frame}   \frametitle{Results: MLB}
  \centering
  \tiny{ % m3, m4
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Probability of Winning} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Continuous measure of nightlife & $-$0.120$^{*}$ &  \\    & (0.071) &  \\    & & \\   Nightlife (no weekend interaction) &  & 0.137 \\    &  & (0.134) \\    & & \\   Bookmaker's odds & 2.682$^{***}$ & 2.669$^{***}$ \\    & (0.158) & (0.158) \\    & & \\   Home-team effect & 0.014 & 0.144 \\    & (0.034) & (0.102) \\    & & \\   Number of rest days & 0.018 & 0.016 \\    & (0.021) & (0.021) \\    & & \\   Logged travel distance & $-$0.005 & $-$0.003 \\    & (0.005) & (0.005) \\    & & \\   Weekend & 0.044 & 0.002 \\    & (0.038) & (0.029) \\    & & \\   Constant & $-$1.363$^{***}$ & $-$1.468$^{***}$ \\    & (0.084) & (0.122) \\    & & \\  \hline \\[-1.8ex]  Observations & 26,473 & 26,473 \\  Log Likelihood & $-$18,124.350 & $-$18,125.300 \\  Akaike Inf. Crit. & 36,272.700 & 36,264.600 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  }
\end{frame}

@@

\begin{frame}   \frametitle{Defense in the NBA}
  \begin{adjustwidth}{-.75cm}{}
  \tiny{  % mpa, tpa, tps
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & Points Admitted by Team & Team Points Admitted & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.817$^{***}$ &  &  \\    & (0.712) &  &  \\    & & & \\   Continuous party measure &  & 1.942$^{***}$ & 0.377 \\    &  & (0.248) & (0.246) \\    & & & \\   Lag change in possessions &  & 0.022$^{***}$ & 0.035$^{***}$ \\    &  & (0.007) & (0.007) \\    & & & \\   Logged travel distance &  & $-$0.411$^{***}$ & 0.035 \\    &  & (0.074) & (0.073) \\    & & & \\   Number hours since last game &  & 0.012$^{***}$ & 0.020$^{***}$ \\    &  & (0.003) & (0.003) \\    & & & \\   Constant & $-$0.046 & 102.824$^{***}$ & 99.540$^{***}$ \\    & (0.091) & (0.483) & (0.478) \\    & & & \\  \hline \\[-1.8ex]  Observations & 15,139 & 44,689 & 44,689 \\  R$^{2}$ & 0.001 & 0.002 & 0.002 \\  Adjusted R$^{2}$ & 0.001 & 0.002 & 0.002 \\  Residual Std. Error & 11.137 (df = 15137) & 12.117 (df = 44684) & 12.015 (df = 44684) \\  F Statistic & 15.670$^{***}$ (df = 1; 15137) & 27.968$^{***}$ (df = 4; 44684) & 24.325$^{***}$ (df = 4; 44684) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}      }
\end{adjustwidth} 
\end{frame}
